Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-25 paper_jasa.tex
type II

\green{Why???? Under the alternative hypothesis, we have to account for different visual abilities of  individuals:} let $X_i$ be a binary random variable with $X_i = 1$, if individual $i$ identifies the data plot from the lineup, and $X_i = 0$ otherwise.  Then $X_i \sim B_{1, p_i}$ and $X = \sum_i X_i$ has  a Poisson-Binomial distribution.

>>>>

\green{Why???? Under the alternative hypothesis, we have to account for different visual abilities of  individuals:} 
\red{I think that's more a matter of writing it - sorry for the confusion - }

let $X_i$ be a binary random variable with $X_i = 1$, if individual $i$ identifies the data plot from the lineup, and $X_i = 0$ otherwise, \red{where $p_i$ is the probability that individual $i$ picks out the data plot from the lineup. 
If all individuals have the same probability $p$ for picking out the data plot, $X = \sum_i X_i$ has distribution $\text{Binom}(K, p)$, and we can estimate $p$ as $\hat{p} = x/K$, where $x$ is the number of observers (out of $K$), who pick out the data plot from the lineup.

If there is evidence for individual skills influencing the probability $p_i$ for picking out the data plot, 
 $X = \sum_i X_i$ has  a Poisson-Binomial distribution.}
